---
output: github_document
---

[![Travis build status](https://travis-ci.org/mdsumner/ncdf4.svg?branch=master)](https://travis-ci.org/mdsumner/ncdf4)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ncdf4

The goal of ncdf4 is to provide an "Interface to Unidata netCDF (Version 4 or Earlier) Format Data Files". 

This fork of the CRAN package `ncdf4` is intended to update the Windows build process, and specifically to add support for Thredds. 

Alternatives: 

* Unidata provides [Visual Studio binaries](https://www.unidata.ucar.edu/downloads/netcdf/index.jsp) that can be used
to put a build together 
* pmjherman has [this repo](https://github.com/pmjherman/r-ncdf4-build-opendap-windows)

## Todo

* check Makevars.win (assume can remove "DHAVE_LIBUDUNITS2" but what about "-DHAVE_DECL_NC_RENAME_GRP=1"?)
* add tests, especially for Thredds (make sure 32-bit Windows limitation is understood)
* roxygenize?

## Installation

You can install the released version of ncdf4 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ncdf4")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/ncdf4")
```
## Example

Read from Thredds (will only work in Windows 64-bit, not 32-bit). 

```{r}
u <- "http://coastwatch.pfeg.noaa.gov/erddap/griddap/erdQSwind3day"
nc <- ncdf4::nc_open(u)
class(nc)
## note that "ncdf" argument is required to trigger use of ncdf4
r <- raster::raster(u, ncdf = TRUE, varname = "x_wind")
print(r)
```
